\documentclass[12pt]{letter} % Default font size of the document, can use values of 10pt, 11pt or 12pt, but you may need to adjust margins if reducing font size

%----------------------------------------------------------------------------------------
%	FONTS
%----------------------------------------------------------------------------------------

\usepackage{helvet}
\usepackage{xcolor}
\renewcommand{\familydefault}{\sfdefault}
\definecolor{primarycolor}{RGB}{65, 105, 225}

%----------------------------------------------------------------------------------------
%	MARGINS
%----------------------------------------------------------------------------------------

\usepackage{geometry} % Required for adjusting page dimensions and margins

\geometry{
	paper=a4paper, % Paper size, change to letterpaper for US letter size
	top=2cm, % Top margin
	bottom=2.5cm, % Bottom margin
	left=3.25cm, % Left margin
	right=3.25cm, % Right margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE
%----------------------------------------------------------------------------------------

\date{\raggedleft\today} % Left-aligned date of the letter, use \today for the current date

\begin{letter}{
	% Name and address of the person to whom the letter is being sent
	Carbon13 Venture Builder Programme \\
	Cambridge, UK
}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS
%----------------------------------------------------------------------------------------

\begin{center}
\color{primarycolor}
\textbf{Karthi Arunachalam \\ 
Cambridge, UK \\
jobs@k18a.org \\
+44-7859745670}
\end{center}

\vspace{1cm} % Vertical whitespace

\signature{Karthi Arunachalam} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	COVER LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Carbon13 Team,}

I am writing to express my strong interest in joining Carbon13's Venture Builder programme as a co-founder committed to building climate tech solutions with 10 million+ tonne CO2e reduction potential.

As someone who has dedicated their entire career to climate impact through technology, Carbon13's mission-driven approach to venture building resonates deeply with my personal and professional values. At age 18, reading Vaclav Smil's "Energy: A Beginner's Guide" sparked my realization that societal progress is fundamentally measured in watts – a principle that has guided my 12+ year journey from First-of-a-Kind climate technologies to market-ready solutions.

Currently, as Senior Research Scientist at SLB's Nerve Center for New Energy research in Cambridge, I manage projects up to \$1M focused specifically on Net Zero technologies. I've led cross-functional teams of up to 8 engineers across material, process, mechanical, and electrical disciplines – experience that has taught me how to navigate the complex technical challenges of scaling climate innovations. My work includes:

\textbf{Climate Technology Leadership:} I've set up fully-automated carbon capture laboratories, developed digital twins for grid-scale energy storage, and created GNN-based frameworks for evaluating low-TRL climate technologies. These projects have given me deep technical expertise in the carbon removal and energy storage sectors that are critical for achieving Net Zero.

\textbf{Startup Evaluation \& Investment:} I regularly analyze and de-risk climate startups and low-carbon technologies for investment decisions, presenting technical due diligence to C-level executives. This experience has given me valuable insight into what makes climate tech ventures successful and fundable.

\textbf{Proven Impact:} At Exactmer, I designed systems that reduced manufacturing carbon footprint by 50\%, demonstrating my ability to translate technical innovation into measurable environmental impact.

What excites me most about Carbon13 is the focus on building ventures with the scale and ambition to achieve 10 million tonne CO2e reduction. Too many climate solutions think incrementally – Carbon13's approach of training founders in deep carbon knowledge and connecting them with world-class technical co-founders creates the foundation for truly transformative impact.

My technical background in carbon capture, energy storage, and process optimization, combined with my experience leading multidisciplinary teams and evaluating climate ventures, positions me to be both a strong technical co-founder and effective collaborator in Carbon13's ecosystem. I'm particularly interested in exploring opportunities at the intersection of carbon removal, energy storage, and industrial decarbonization – areas where my expertise could contribute to building ventures with genuine gigatonne-scale potential.

\closing{I would welcome the opportunity to discuss how my experience in scaling climate technologies from laboratory to commercial deployment could contribute to Carbon13's mission. I'm ready to commit fully to building the climate solutions our planet urgently needs.}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}