\documentclass{../../templates/karthicv-single}
\usepackage{color}
\setlength{\parindent}{0pt}

% Update your contact details here
\renewcommand{\cvname}{Karthi Arunachalam}
\renewcommand{\cvemail}{k18a@pm.me}
\renewcommand{\cvphone}{+44-7859745670}
\renewcommand{\cvheadline}{Founder and Scientist on a mission to Solve the Climate Crisis with AI and Engineering}
\renewcommand{\cvwebpage}{https://www.linkedin.com/in/k8r/}
\renewcommand{\cvaddress}{Cambridge, UK}

\begin{document}

\maketitle

\vspace{-1em}
\begin{center}
\textit{I turn scientific rigour into shipped climate products. Over the past 12 years, I've helped scale FOAK climate-tech into production systems — blending real-world experimentation, energy system modeling, and AI. At 18, I read Vaclav Smil's words: "Societal progress is measured in watts." That line shaped my life — and it still defines my mission today.}
\end{center}

\section{Experience}
\experience{Founder}{ExerVolt - Stealth}{Cambridge, UK}{9/25-Present}
{Working with Carbon13 in Cambridge, I started working on a new startup focused on long duration energy storage.\\
Built a digital twin of an initial MVP to evaluate initial beach head markets in UK and India. \\
Worked with industry experts to iteratively refine the product-market fit through customer discovery interviews and iterative model development.\\
Developed specialized AI models and data architectures to assist with technology optimization, techno-economic analysis, and market discovery.}

\experience{Senior Research Scientist}{SLB}{Cambridge, UK}{9/21-Present}
{Based out of SLB's \textbf{Nerve Center for New Energy research}, managed research projects up to \$1M targeting \textbf{Net Zero technologies}. \\
Led cross-functional teams of up to 8 engineers across material, process, mechanical, and electrical disciplines. \\
Developed AI models to \textbf{predict climate tech success under uncertainty} (Bayesian + GNNs) \\
Analyzed and de-risked \textbf{low-carbon technologies and climate startups} towards investment decisions; presented updates to C-level stakeholders. \\
Set up a fully-automated \textbf{carbon capture laboratory} to de-risk new CO2 removal technologies and materials. \\
Developed \textbf{digital twins for energy storage} devices to optimize battery management systems for grid-scale deployment. \\
Developed carbon dioxide sensors for HPHT applications - successfully \textbf{integrated within client's industrial processes}. \\
Recruited and mentored interns and new hires across multidisciplinary climate tech projects.}

\experience{Chemical Engineer}{Exactmer}{London, UK}{2/21-9/21}
{Developed automation and control systems for oligonucleotide synthesizers in pharmaceutical manufacturing. \\
Designed and implemented a \textbf{solvent recovery system reducing manufacturing carbon footprint by 50\%}. \\
Built \textbf{Industry 4.0 process dashboards} using OPCUA and Plotly Dash for real-time manufacturing optimization. \\
Participated in HAZOPs as automation expert, ensuring safe scale-up of pharmaceutical processes.}

\experience{PhD Researcher}{University of Edinburgh}{Edinburgh, UK}{9/16-2/21}
{Researched \textbf{CO2 sequestration in geological formations} through reactive transport modeling of gas flow in microporous shales. \\
\textbf{Designed, built, and commissioned} HPHT multi-component gas sorption systems for carbon storage research. \\
Published research at \textbf{international conferences and journals} on carbon dioxide storage mechanisms. \\
Taught undergraduate Mass Transfer, developing future engineers for clean energy applications.}

\experience{Production Technology Specialist}{Schlumberger}{Barmer, India}{7/15-3/16}
{Managed environmental and safety risks in India's largest onshore oilfield, focusing on \textbf{H2S emission control}.}

\experience{Process Engineer}{Petro6 EC}{Chennai, India}{12/09-8/13}
{Designed 10,000 bopd process train and control systems for energy infrastructure projects.}

\section{Skills}

\textbf{Climate Technology}: \\
Carbon capture and storage, CO2 sensors, energy storage systems, digital twins, grid optimization \\
\textbf{Technical Leadership}: \\
Cross-functional team management (8+ engineers), project management (\$1M+ budgets), startup evaluation \\
\textbf{Machine Learning \& AI}: \\
Python, TensorFlow, PyTorch, Graph Neural Networks, techno-economic modeling, Bayesian analysis \\
\textbf{Engineering \& Product}: \\
Process design, automation, Industry 4.0, HAZOP, control systems, manufacturing optimization \\

\section{Education}
\cventry{AI Professional Program}{Stanford University}\\
\textit{Machine Learning with Graphs specialization (96\%)} \hfill 2024-25\\
\cventry{PhD Engineering}{University of Edinburgh}\\
\textit{CO2 sequestration and carbon storage research} \hfill 2021\\
\cventry{CFA Level 1}{CFA Institute}\\
\textit{Financial analysis for climate technology investments} \hfill 2018\\
\cventry{MSc Management}{University of Aberdeen}\\
\textit{Business strategy and operations management} \hfill 2015\\
\cventry{BEng Chemical Engineering}{Anna University}\\
\textit{Process engineering and energy systems} \hfill 2013\\

\section{Climate Leadership \& Voluntary Experience}

\experience{Committee Member}{IChemE Clean Energy SIG}{UK}{7/23-3/25}
{Leading outreach activities to promote chemical engineering applications in \textbf{clean energy and Net Zero technologies}.}
\experience{Member}{SLB Empowerment Team}{Cambridge, UK}{1/22-12/23}
{Led campaigns and audits to enhance HSE KPIs and \textbf{sustainable operations practices}.}
\experience{Secretary}{IChemE Scottish MG}{Edinburgh, UK}{5/17-6/19}
{Oversaw and co-ordinated group activities alongside chair. Led Committee meetings and Organized AGMs.}
\experience{MSc Researcher}{University of Aberdeen}{Aberdeen, UK}{1/14-9/14}
{Conducted \textbf{DCF analysis of carbon capture and storage plant} to determine carbon pricing mechanisms for policy development.}

\section{Publications \& Research Impact}
Impact of heat of sorption on thermal enhanced recovery of sorbed gas from gas shale reservoirs – An experimental and simulation study. K Arunachalam, X Fan, 2020, \textbf{Journal of Natural Gas Science and Engineering} \\
Implications of Sorption on Carbon dioxide Sequestration in Gas Shales. K Arunachalam, X Fan, 2020, \textbf{COMSOL International Conference}

\section{Entrepreneurial Impact \& Vision}
\textbf{Track Record}: 12+ years scaling First-of-a-Kind climate technologies into market-ready solutions. \\
\textbf{Technical Leadership}: Led multidisciplinary teams from research through commercial deployment. \\
\textbf{Investment Expertise}: Evaluated climate startups and low-carbon technologies for commercial viability.\\
\textbf{Prototypes under Construction}: \textbf{ScopeFlow}: Automated CSDR reporting with eventual vision to become vertical SaaS for carbon reporting; \textbf{Etherium}: Memory System for Intelligent Systems. \\

\end{document}
